\huge Tor's Usability for Censorship Circumvention

### 2016-04-18 pets2017-paper/pets2017-paper.tex
hastily done results section

\subsubsection{Rate of Success} 
Distribution of success times. Figure~\ref{fig:time_to_success_clamped}

%stats
impact of version on success: not significant (W = 5.5, p-value = 0.8248)
impact of env on success: not significant (Kruskal-Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)

\begin{table}[t]
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\ % medians of only finished: 0:20 
	E1-OLD & 19/19 & 100\% & 1:01 \\ %medians of only finished: 1:01
	E2-NEW & 18/19 & 95\% & 3:32 \\ %medians of only finished: 3:22
	E2-OLD & 16/19 & 84\% & 5:00 \\ %medians of only finished: 3:13
	E3-NEW & 13/20 & 65\% & 20:56 \\ %medians of only finished: 12:38
	E3-OLD & 10/20 & 50\% & 40:08 \\ %medians of only finished: 18:16 
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

\begin{table}[t]
\centering
% Generated by attempts.R, and manually reordered:
\begin{tabular}{r c c c c c c}
& \rotatebox{90}{E1-NEW} & \rotatebox{90}{E1-OLD} & \rotatebox{90}{E2-NEW} & \rotatebox{90}{E2-OLD} & \rotatebox{90}{E3-NEW} & \rotatebox{90}{E3-OLD} \\
no bridge, no proxy & 17 & 13 &  &  &  &  \\
obfs3, no proxy & 2 & 6 & 18 & 16 &  &  \\
meek-amazon, no proxy &  &  &  &  & 7 & 4 \\
meek-google, no proxy &  &  &  &  & 5 & 4 \\
meek-azure, no proxy &  &  &  &  & 1 & 1 \\
no bridge, 3rd-party proxy &  &  &  &  &  & 1 \\
DNF &  &  & 1 & 3 & 7 & 10 \\
\end{tabular}
\caption{
Bridge--proxy combinations that led to the first successful bootstrap
in each environment and interface.
Most E1 participants used a direct connection,
but a few tried a built-in obfs3 bridge.
All the E2 participants who succeeded,
did so with obfs3 (the recommended bridge type)---none tried
a different bridge before obfs3.
All of the successful E3 participants, but one,
used one of the meek bridges.
The remaining E3 participant succeeded in an unexpected way:
by searching the web for an open proxy and configuring it
as the proxy setting.
}
\label{tab:attempts-bridge-proxy}
\end{table}

\subsubsection{Time to Success}

impact of version on time to success: not significant (W = 1399, p-value = 0.1175)
impact of env on time to success : significant ( Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)

@@

Our participants had 40 minutes. In real life, people may give up a lot sooner. 
Figure~\ref{fig:time_to_success_ecdf}. Table~\ref{table:less_time}.

\begin{figure}
\centering
\includegraphics{time_to_success_ecdf}
\caption{
Cumulative success rates over time, by censorship environment and interface.
We stopped participants after 40 minutes. Those who did not finish were assigned
an arbitrarily high number greater than 40 minutes. 
}
\label{fig:time_to_success_ecdf}
\end{figure}

@@

\subsubsection{Additional information} 
While we did not find a statistically significant difference between the overall time to success between the old and new versions of the interface, the time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface. Table ~\ref{table:overall_time} shows the time spent on each screen while participants used the interface, which shows that participants spent 57\% of their overall time at the progress screen.

@@

We define the time participants not on the progress screen as the amount of time they actively spent configuring their connection. This is a simplified notion the time participants spent configuring, since some participants waited at the progress screen without doing anything while others searched for help on the web while they were waiting. However, participants with the new and old interface were equally likely to exhibit this behavior. Participants with the new interface showed a statistically significant reduction in the overall time configuring the interface (Mann-Whitney W = 997, p-value = 0.0001571). 
%The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)

We summarize each participant's actions throughout the experiment in Figure~\ref{fig:all-participant-edges}. Each row in Figure~\ref{fig:all-participant-edges} corresponds to a participant in our experiment. The bar represents a participants' path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.

@@

% impacts of making the proxy page ``automated'' 
\item {\bfseries Users wasted time configuring proxies.} Overall, 57\% of participants' active time was spent configuring proxies. Participants with the new interface spent 31\% of their active time configuring proxies and participants in the old interface spent 63\%.

@@

% progress bar
\item {\bfseries Users with the new interface waited longer.}
Participants with the new interface the new interface spent more time waiting in the progress bar, proportionally and absolutely. 
\end{description}

@@

\subsubsection{Recommendations}
Based on our observations of general behavioral trends and common failure cases, we make the following recommendations to increase success rate and decrease overall time spent in the interface: \\

>>>>

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\ % medians of only finished: 0:20 
	E1-OLD & 19/19 & 100\% & 1:01 \\ %medians of only finished: 1:01
	E2-NEW & 18/19 & 95\% & 3:32 \\ %medians of only finished: 3:22
	E2-OLD & 16/19 & 84\% & 5:00 \\ %medians of only finished: 3:13
	E3-NEW & 13/20 & 65\% & 20:56 \\ %medians of only finished: 12:38
	E3-OLD & 10/20 & 50\% & 40:08 \\ %medians of only finished: 18:16 
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

\subsubsection{Rate of Success} 
5 more participants with the new interface were able to successfully circumvent censorship and connect to the Tor network. Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference. However, this does suggest that users are not less likely to succeed with the new interface based on the changes that were made. 
% impact of version on success: not significant (Mann-Whitney W = 5.5, p-value = 0.8248)
%impact of env on success: not significant (Kruskal-Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)

Table~\ref{tab:attempts-bridge-proxy} shows the configuration settings of the first successful bootstrap in each environment and interface combination. Note that only four of the default bridges were used to connect successfully for the first time. Users avoid making decisions when a recommendation is given and tend to avoid/fail with more advanced options. Participants who were in environments in that the recommended bridge (obfs3) worked did not configure another bridge, not taking advantage of the various default bridges available to them. Participants who were in environment that required a meek or custom bridge only were able to succeed with a meek-bridge.

\begin{table}
\centering
% Generated by attempts.R, and manually reordered:
\begin{tabular}{r c c c c c c}
& \rotatebox{90}{E1-NEW} & \rotatebox{90}{E1-OLD} & \rotatebox{90}{E2-NEW} & \rotatebox{90}{E2-OLD} & \rotatebox{90}{E3-NEW} & \rotatebox{90}{E3-OLD} \\
no bridge, no proxy & 17 & 13 &  &  &  &  \\
obfs3, no proxy & 2 & 6 & 18 & 16 &  &  \\
meek-amazon, no proxy &  &  &  &  & 7 & 4 \\
meek-google, no proxy &  &  &  &  & 5 & 4 \\
meek-azure, no proxy &  &  &  &  & 1 & 1 \\
no bridge, 3rd-party proxy &  &  &  &  &  & 1 \\
DNF &  &  & 1 & 3 & 7 & 10 \\
\end{tabular}
\caption{
Bridge--proxy combinations that led to the first successful bootstrap
in each environment and interface.
Most E1 participants used a direct connection,
but a few tried a built-in obfs3 bridge.
All the E2 participants who succeeded,
did so with obfs3 (the recommended bridge type)---none tried
a different bridge before obfs3.
All of the successful E3 participants, but one,
used one of the meek bridges.
The remaining E3 participant succeeded in an unexpected way:
by searching the web for an open proxy and configuring it
as the proxy setting.
}
\label{tab:attempts-bridge-proxy}
\end{table}

\subsubsection{Time to Success} 
Although the median times to completion for participants of the new interface are less than those with the old interface (Table~\ref{table:participant-summary}), this difference is not statistically significant. The level of censorship had a significant impact on the time to success. The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16). The distribution of participants' time to success can be seen in Figure~\ref{fig:time_to_success_clamped}.
%impact of version on time to success: not significant (W = 1569, p-value = 0.07796)
%impact of env on time to success : significant (Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)

@@

In our experiment, participants had 40 minutes to circumvent censorship. Figure~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time. Participants were less and less likely to succeed as time went on. Users in the wild will likely not be motivated to configure their connection for 40 minutes. Table~\ref{table:less_time} shows that if users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments will be unable to connect. Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments will be unable to connect. Ideally, users should be able to connect to Tor within a couple of minutes, regardless of their censorship environment. We propose ideas on how to achieve this in section~\ref{recommendations}.

\begin{figure}
\centering
\includegraphics{time_to_success_ecdf}
\caption{
Cumulative success rates over time, by censorship environment and interface.
We stopped participants after 40 minutes. Here, those who did not finish were assigned
an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
}
\label{fig:time_to_success_ecdf}
\end{figure}

@@

\subsubsection{Additional information} 
We summarize each participant's actions throughout the experiment in Figure~\ref{fig:all-participant-edges}. Each row in Figure~\ref{fig:all-participant-edges} corresponds to a participant in our experiment. The bar represents a participants' path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.

While we did not find a statistically significant difference between the overall time to success between the old and new versions of the interface, the time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface. Table ~\ref{table:overall_time} shows the time spent on each screen while participants used the interface, which shows that participants spent 57\% of their overall time at the progress screen. Participants using the new interface and old interface waited spent approximately the same amount of time overall on the progress screen (359 minutes versus 339 minutes), which accounts for 78\% and 45\% of their overall time, respectively. We attribute this to a combination of instructions that tell the user to ``wait a couple minutes'' because connections usually take a while to bootstrap and the lack of timeout on the progress screen which keeps the users waiting indefinitely, which were present in both versions of the interface.

@@

Perhaps a more meaningful measurement of time is the amount of times participants actively spent configuring their connection. We define this as the amount of time that participants spent on the interface, except for time spent on the progress screen. This is a simplified notion active configuration time, since some participants searched for help on the web while they were waiting. However, this behavior was equally likely in the new and old interface conditions.

The new interface results a statistically significant reduction in the overall active configuration time (Mann-Whitney Z = -3.055, p-value = 0.00225, effect size = 0.284), while maintaining the same probability for success for the user. We believe that getting rid of the technical bridge and proxy questions, instructing participants that they did not need a proxy, and simplifying the interface attributed to the reduction in time. 
%The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)

@@

% impacts of making the proxy page ``automated'' 
\item {\bfseries Users wasted time configuring proxies.} Overall, 57\% of participants' active configuration time was spent on the proxy screens. Participants with the new interface spent 31\% of their active time configuring proxies and participants in the old interface spent 63\%.

@@

% progress bar
\item {\bfseries People waited a long, long time at the progress bar.}
From observing videos, participants genuinely wait, dutifully following the directions.   
\end{description}

@@

\subsubsection{Recommendations}
\label{recommendations}
Based on our observations of general behavioral trends and common failure cases, we make the following recommendations to increase success rate and decrease overall time spent in the interface: \\
